---
title: "LoadIndicators"
author: "Alex Frye, Chris Boomhower"
date: "July 20, 2016"
output: md_document
---

```{r read_chunk_LoadIndicators, cache=FALSE}
knitr::read_chunk(paste0(DataLoad,'/LoadIndicators.R'))
```

Finally, the third data set loaded is the Chulwar external indicator data. Again, the data set has been sourced from the SMU 2DS platform Unit 10.2 Overview page:

```{r LoadIndicators}
```

Reviewing the external indicator data post-import confirms successful loading.

As before, review indicates there are multiple groups (Export Price Changes, Satisfaction Index (Gov), Average Temperature, Births, Satisfaction Index (Independent), Total Exports from Urbano, Globalization Party Members, Average Export Price, Etel Production Price Index, Chulwalar Index, Inflation, Spending for Chulwalar Days, Chulwalar Days, and Influence of Chulwalar Days) of data within the single CSV file that need split by group. In order to do so, these data once again need parsed during cleanup and assigned to a data frame before analysis.
