---
title: "CleanAsIs"
author: "Alex Frye, Chris Boomhower"
date: "July 16, 2016"
output: md_document
---

To clean our As Is Chulwar data, we need to first separate each export group (e.g. Total, Efak, Wuge, etc.) into individual vectors.
Since the only group that has data for 2014 is "Total", we have created a separate variable for just TotalAsIs_2014 data. 

```{R CleanAsIs_toVector}
TotalAsIsVector <- c(AsIsChulwar [2:13, 2],
                     AsIsChulwar [2:13, 3],
                     AsIsChulwar [2:13, 4],
                     AsIsChulwar [2:13, 5],
                     AsIsChulwar [2:13, 6],
                     AsIsChulwar [2:13, 7])

EfakAsIsVector <- c(AsIsChulwar [16:27, 2],
                    AsIsChulwar [16:27, 3],
                    AsIsChulwar [16:27, 4],
                    AsIsChulwar [16:27, 5],
                    AsIsChulwar [16:27, 6],
                    AsIsChulwar [16:27, 7])

WugeAsIsVector <- c(AsIsChulwar [30:41, 2],
                    AsIsChulwar [30:41, 3],
                    AsIsChulwar [30:41, 4],
                    AsIsChulwar [30:41, 5],
                    AsIsChulwar [30:41, 6],
                    AsIsChulwar [30:41, 7])

TotalEtelAsIsVector <- c(AsIsChulwar [44:55, 2],
                         AsIsChulwar [44:55, 3],
                         AsIsChulwar [44:55, 4],
                         AsIsChulwar [44:55, 5],
                         AsIsChulwar [44:55, 6],
                         AsIsChulwar [44:55, 7])

BlueEtelAsIsVector <- c(AsIsChulwar [58:69, 2],
                        AsIsChulwar [58:69, 3],
                        AsIsChulwar [58:69, 4],
                        AsIsChulwar [58:69, 5],
                        AsIsChulwar [58:69, 6],
                        AsIsChulwar [58:69, 7])

RedEtelAsIsVector <- c(AsIsChulwar [72:83, 2],
                       AsIsChulwar [72:83, 3],
                       AsIsChulwar [72:83, 4],
                       AsIsChulwar [72:83, 5],
                       AsIsChulwar [72:83, 6],
                       AsIsChulwar [72:83, 7])

YearAsIsVector <- c(AsIsChulwar [86, 2],
                    AsIsChulwar [86, 3],
                    AsIsChulwar [86, 4],
                    AsIsChulwar [86, 5],
                    AsIsChulwar [86, 6],
                    AsIsChulwar [86, 7])

TotalAsIsVector_2014 <- c(AsIsChulwar[2:13, 8])
```

Second, we need to convert each new vector into a time series.

```{r CleanAsIs_toTimeSeries}
# The data is saved as a vector and needs to be converted into a time series
TotalAsIs <- ts(
                TotalAsIsVector,
                start             = c(2008, 1),
                end               = c(2013, 12),
                frequency         = 12
               )

EfakAsIs <- ts(
               EfakAsIsVector ,
               start              = c(2008, 1),
               end                = c(2013, 12),
               frequency          = 12
              )

WugeAsIs <- ts(
               WugeAsIsVector,
               start              = c(2008, 1),
               end                = c(2013, 12),
               frequency          = 12
              )

TotalEtelAsIs <- ts(
                    TotalEtelAsIsVector,
                    start         = c(2008, 1),
                    end           = c(2013, 12),
                    frequency     = 12
                   )

BlueEtelAsIs <- ts(
                   BlueEtelAsIsVector,
                   start          = c(2008, 1),
                   end            = c(2013, 12),
                   frequency      = 12
                  )
RedEtelAsIs <- ts(
                  RedEtelAsIsVector,
                  start           = c(2008, 1),
                  end             = c(2013, 12),
                  frequency       = 12
                )
YearAsIs <- ts(
               YearAsIsVector,
               start              = c(2008, 1),
               end                = c(2013, 12),
               frequency          = 12
              )

TotalAsIs_2014 <- ts(
                     TotalAsIsVector_2014,
                     start        = c(2014, 1),
                     end          = c(2014, 12),
                     frequency    = 12
                    )
```

With our time series variables created for each export group, lets review the data for each to ensure it matches our expectations.

```{r CleanAsIs_ReviewData}
TotalAsIs
EfakAsIs
WugeAsIs
TotalEtelAsIs
BlueEtelAsIs
RedEtelAsIs
YearAsIs
TotalAsIs_2014
```
