---
title: "CleanPlan"
author: "Alex Frye, Chris Boomhower"
date: "July 16, 2016"
output: md_document
---

Upon completing basic EDA to gain understanding for how many groups of export item data there are in the Chulwalar plan data, the first order of business is to parse the data and to divide each export item's content into separate vectors to be used during the analysis

```{r PlanVectors}
PlanVector <-
  c(
  CWplan[2:13, 2],
  CWplan[2:13, 3],
  CWplan[2:13, 4],
  CWplan[2:13, 5],
  CWplan[2:13, 6],
  CWplan[2:13, 7]
  )
  EfakPlanVector <-
  c(
  CWplan[16:27, 2],
  CWplan[16:27, 3],
  CWplan[16:27, 4],
  CWplan[16:27, 5],
  CWplan[16:27, 6],
  CWplan[16:27, 7]
  )
  WugePlanVector <-
  c(
  CWplan[30:41, 2],
  CWplan[30:41, 3],
  CWplan[30:41, 4],
  CWplan[30:41, 5],
  CWplan[30:41, 6],
  CWplan[30:41, 7]
  )
  TotalEtelPlanVector <-
  c(
  CWplan[44:55, 2],
  CWplan[44:55, 3],
  CWplan[44:55, 4],
  CWplan[44:55, 5],
  CWplan[44:55, 6],
  CWplan[44:55, 7]
  )
  BlueEtelPlanVector <-
  c(
  CWplan[58:69, 2],
  CWplan[58:69, 3],
  CWplan[58:69, 4],
  CWplan[58:69, 5],
  CWplan[58:69, 6],
  CWplan[58:69, 7]
  )
  RedEtelPlanVector <-
  c(
  CWplan[72:83, 2],
  CWplan[72:83, 3],
  CWplan[72:83, 4],
  CWplan[72:83, 5],
  CWplan[72:83, 6],
  CWplan[72:83, 7]
  )
  YearPlanVector <-
  c(
  CWplan[86, 2],
  CWplan[86, 3],
  CWplan[86, 4],
  CWplan[86, 5],
  CWplan[86, 6],
  CWplan[86, 7]
  )
  PlanVector_2014 <- c(CWplan[2:13, 8])
```

With the various planned export groups' data being divided into unique vectors, the next step is to convert the vectors to time-series format.

```{r planTimeSeries}
TotalPlan <-
  ts(
  PlanVector ,
  start = c(2008, 1),
  end = c(2013, 12),
  frequency = 12
  )
  EfakPlan <-
  ts(
  EfakPlanVector,
  start = c(2008, 1),
  end = c(2013, 12),
  frequency = 12
  )
  WugePlan <-
  ts(
  WugePlanVector,
  start = c(2008, 1),
  end = c(2013, 12),
  frequency = 12
  )
  TotalEtelPlan <-
  ts(
  TotalEtelPlanVector,
  start = c(2008, 1),
  end = c(2013, 12),
  frequency = 12
  )
  BlueEtelPlan <-
  ts(
  BlueEtelPlanVector,
  start = c(2008, 1),
  end = c(2013, 12),
  frequency = 12
  )
  RedEtelPlan <-
  ts(
  RedEtelPlanVector,
  start = c(2008, 1),
  end = c(2013, 12),
  frequency = 12
  )
  YearPlan <-
  ts(
  YearPlanVector,
  start = c(2008, 1),
  end = c(2013, 12),
  frequency = 12
  )
  TotalPlan_2014 <-
  ts(
  PlanVector_2014,
  start = c(2014, 1),
  end = c(2014, 12),
  frequency = 12
  )
```

Now that the data have been converted to time-series format, it is important to verify the conversion was made correctly.

```{r PlanTSverify}
TotalPlan
EfakPlan
WugePlan 
TotalEtelPlan
BlueEtelPlan
RedEtelPlan
YearPlan
TotalPlan_2014
```

The data is now clean and ready for further analysis.