---
title: "README"
author: Alex Frye
output: 
  md_document
---

```{r DeclarePath, echo=  FALSE}
##Change this path per your project root directory on your machine if you wish to regen the README.html file
DefaultDir<-"D:/Documents/School/SMU/2016 Summer/MSDS 6306 - Into to Data Science/Assignments/Week 10/MSDS6306_CaseStudy10_Afrye_CBoomhower"

RResourcesDir<-paste(DefaultDir,"/RResources",sep = "")
```

##Assignment Definition
Assignment Text.....


##FILE TREE STRUCTURE DEFINED
```{r Twee, echo = FALSE}
setwd(DefaultDir)
source(paste(RResourcesDir,"/twee.R",sep = ""))
twee()
```

**NOTE:** Project Deliverable File Located: "~/Paper/CaseStudy10_Paper.MD"

##PROJECT REPRODUCIBILITY INSTRUCTIONS

1. Regenerate README (If Project File Structure Changes)
    + Open README.RMD located inside Project Root
    + Modify DefaultDir input to your Project's Root Directory Path
    + Knit README.Rmd
2. Regenerate AFrye_Week6CaseStudy.MD
    + Open CaseStudy10_Paper.RMD
    + Modify DefaultDir input to your Project's Root Directory Path
    + Ensure all required R Packages are installed on your machine. Uncomment any needed Install.Packages code lines
    + Knit CaseStudy10_Paper.RMD
