---
title: "README"
author: Alex Frye
output: 
  md_document
---

```{r DeclarePath, echo=  FALSE}
##Change this path per your project root directory on your machine if you wish to regen the README.html file
DefaultDir<-"C:\\Users\\Owner\\Documents\\GitHub\\MSDS_6306\\MSDS6306_CaseStudy10_Afrye_CBoomhower"

RResourcesDir<-paste(DefaultDir,"/RResources",sep = "")
```

##Assignment Definition
The prime minister of Chulwalhar has asked us to help him in forecasting exports from his country. In order to do this we have been given as-is data, which is the original or observed data, and planned data, which is what Chulwalhar would like to export. We also have a list of indicators that may affect exports. Our job is to find out the best way to forecast Chulwalhar’s exports in 2014 based on data collected before this year. In other words, we want to create a credible statistical model.

The export data for Chulwalhar are in two CSV files. One contains the as-is data and the other one contains the planned data. These data sets are also composed of other data sets: monthly and yearly for both groups. Your task is to take all of these data sets, import them into R, and develop a model to forecast the exports of these particular products for the prime minister of Chulwalhar.

Submit an R markdown document with the code necessary to download clean and analyze the data. Interpretations of the code and analysis should be provided. There should also be at least one graphic that explains an important feature of the data. This graphic should be interpreted in the text of the document.


##FILE TREE STRUCTURE DEFINED
```{r Twee, echo = FALSE}
setwd(DefaultDir)
source(paste(RResourcesDir,"/twee.R",sep = ""))
twee()
```

**NOTE:** Project Deliverable File Located: "~/Paper/CaseStudy10_Paper.MD"

##PROJECT REPRODUCIBILITY INSTRUCTIONS

1. Regenerate README (If Project File Structure Changes)
    + Open README.RMD located inside Project Root
    + Modify DefaultDir input to your Project's Root Directory Path
    + Knit README.Rmd
2. Regenerate AFrye_Week6CaseStudy.MD
    + Open CaseStudy10_Paper.RMD
    + Modify DefaultDir input to your Project's Root Directory Path
    + Ensure all required R Packages are installed on your machine. Uncomment any needed Install.Packages code lines
    + Knit CaseStudy10_Paper.RMD
