---
title: "EfakSmoothing"
author: "Alex Frye, Chris Boomhower"
date: "July 19, 2016"
output: md_document
---

```{r read_chunk_EfakSmoothing, cache=FALSE, include=FALSE}
knitr::read_chunk(paste0(DataAnalysis,'/EfakSmoothing.R'))
```

Now that all EDA steps are complete, we are ready to run our forecast models. Several models are available for time series forecasting. The models used in this analysis are:

* Simple Exponential Smoothing (SES)
* Holt's Linear Trend (HLT)
* Holt's Exponential Trend (HET)
* Holt's Damped Linear Trend (HDLT)
* Holt's Damped Exponential Trend (HDET)
* Holt-Winters' Seasonal Additive Model (HWSA)
* Holt-Winters' Seasonal Multiplicative Model (HWSM)

```{r ExecAllSmooth}
```

The Akaike’s Information Criterion (AIC), Akaike's Information Criterion Corrected (AICc), and Bayesian Information Criterion (BIC) are Maximum Likelihood Estimators (MLE). These are important measures of goodness of fit, and as such, their values are extracted from each model's summary output and assigned to a data frame for later analysis. The resulting data frame is as follows.

Minimum AIC/AICc/BIC values are highlighted in green, representing the best goodness of fit for the corresponding models. The Holt-Winters' Seasonal Additive Model contains the lowest AIC and AICc values whereas the Simple Exponential Smoothing model has the lowest value for BIC. Given that the Holt-Winters' Seasonal Additive and Simple Exponential Smoothing models have the smallest values, this is an early indicator that these models may be the best fit for Efak as-is data.

```{r ComputeModelMLE, include=FALSE}
```

```{r ComputeModelMLEtable, echo=FALSE}
```

To further illustrate the difference in MLE measures, the AIC/AICc/BIC values are plotted for each model type. As indicted in the previous table, the Holt-Winters' Seasonal Additive and Simple Exponential Smoothing models depict the smallest measures. It is worth noting that the Holt-Winters' Seasonal Additive model has the second smallest BIC value and that while its multiplicative version has the second smallest AIC/AICc values, the multiplicative model portrays the largest BIC value. For these reasons, it is important to consider all available measures holistically as will be done further momentarily.

```{r plotModelMLE}
```

Similar to AIC/AICc/BIC measures, various summary measures of forecast accuracy exist in the form of error values. The error measures used in this analysis are:

* Mean Error (ME)
* Root Mean Squared Error (RMSE)
* Mean Absolute Error (MAE)
* Mean Percentage Error (MPE)
* Mean Absolute Percentage Error (MAPE)
* Mean Absolute Scaled Error (MASE)
* Autocorrelation of Errors at Lag 1 (ACF1)



```{r ComputeModelError, include=FALSE}
```

```{r ComputeModelErrorTable}
```

```{r SimpleExponential}
```

```{r HoltLinear}
```

```{r HoltExponential}
```

```{r HoltDampedLinear}
```

```{r HoltDampedExponential}
```

```{r HoltWinterSeasonalAdd}
```

```{r HoltWinterSeasonalMult}
```

