---
title: "CaseStudy10_Paper"
author: "Alex Frye, Chris Boomhower"
date: "July 16 2016"
output: md_document
---

```{r DefineDirectory, include=FALSE}
##Change this path per your project root directory on your machine if you wish to regen the CaseStudy10_Paper.md file

###"D:/Documents/School/SMU/2016 Summer/MSDS 6306 - Into to Data Science/Assignments/Week 10/MSDS6306_CaseStudy10_Afrye_CBoomhower"

###"C:/Users/Owner/Documents/GitHub/MSDS_6306/MSDS6306_CaseStudy10_Afrye_CBoomhower"

DefaultDir<-"C:/Users/Owner/Documents/GitHub/MSDS_6306/MSDS6306_CaseStudy10_Afrye_CBoomhower"
DataLoad<-paste(DefaultDir,"/DataLoad",sep = "")
DataCleanup<-paste(DefaultDir,"/DataCleanup",sep = "")
DataAnalysis<-paste(DefaultDir,"/DataAnalysis",sep = "")
RResources<-paste(DefaultDir,"/RResources",sep = "")
####source(paste0(RResources,'/SourceAll.R'))
```


#Introduction

Intro Text goes here.......

###Required Packages

This RMD requires the following R packages to run:

* formattable
* fpp

If you do not currently have installed any of these packages, please uncomment the install.packages lines below before knitting this file.

**This list is for different project...need to clean up as we go...**

```{R Install_Load_Pkgs, message=FALSE}
#install.packages("formattable")
#install.packages("fpp")

library(formattable)
library(fpp)
```

#Data Load

Data Load Intro Text goes here.....

###AsIs Chulwalar Data 
``` {r data, child = paste(DataLoad,"/LoadAsIs.rmd",sep = "")}
```

###Plan Chulwalar Data 
``` {r data, child = paste(DataLoad,"/LoadPlan.rmd",sep = "")}
```


#Data Cleanup

Data cleanup is imperative to any data analysis. In our precursory view into header/footer records, we can tell there are several items needing to be cleaned across the two datasets. The following sections will walk through cleaning the data to prep for analysis.

###AsIs Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanAsIs.rmd",sep = "")}
```

###Plan Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanPlan.rmd",sep = "")}
```

#Data Analysis & Questions

Analysis text...

Add RMD files for analysis...did not create these yet so left out of paper for now.

#Conclusion

Conclusion Text Goes Here....