---
title: "CaseStudy10_Paper"
author: "Alex Frye, Chris Boomhower"
date: "July 16 2016"
output: md_document
---

```{r DefineDirectory, include=FALSE}
##Change this path per your project root directory on your machine if you wish to regen the CaseStudy10_Paper.md file

###"D:/Documents/School/SMU/2016 Summer/MSDS 6306 - Into to Data Science/Assignments/Week 10/MSDS6306_CaseStudy10_Afrye_CBoomhower"

###"C:\\Users\\Owner\\Documents\\GitHub\\MSDS_6306\\MSDS6306_CaseStudy10_Afrye_CBoomhower"

DefaultDir<-"C:\\Users\\Owner\\Documents\\GitHub\\MSDS_6306\\MSDS6306_CaseStudy10_Afrye_CBoomhower"
DataLoad<-paste(DefaultDir,"/DataLoad",sep = "")
DataCleanup<-paste(DefaultDir,"/DataCleanup",sep = "")
DataAnalysis<-paste(DefaultDir,"/DataAnalysis",sep = "")
RResources<-paste(DefaultDir,"/RResources",sep = "")
###source(paste0(RResources,'/SourceAll.R'))
```


#Introduction

Our client, the prime minister of Chulwalar has recruited our small team of SMU data scientists to assist in forecasting Efak (A beautiful flower unique to the region of Chulwalar) exports from his country. He has provided us with historical, as-is flower export data, planned export data, and external key indicators unique to Chulwalar (All historical data provided by month from 2008-2013). It is our duty to best forecast Chulwalar Efak exports in the upcoming year (2014) based on existing export data.

There are several steps needed to accomplish this task. These steps are summarized as follows:

* Load all data sets
* Clean and prepare as-is, planned, and external indicator data for analysis
* Observe correlation between as-is and planned exports
* Plot seasonal and trend decomposition using Loess (STL) for as-is export data
* Plot seasonal trends by month
* Perform exploratory data analysis (EDA) to better understand effects of external indictors
* Utilize smoothing techniques to forecast future exports

###Required Packages

This RMD requires the following R packages to run:

* formattable
* fpp
* ggplot2
* reshape2

```{R Install_Load_Pkgs, message=FALSE, include = FALSE}
#install.packages("formattable")
#install.packages("fpp")
#install.packages("ggplot2")
#install.packages("reshape2")

library(formattable)
library(fpp)
library(ggplot2)
library(reshape2)
```

#Data Load

As this analysis consists of historical export data, planned data, and external indicator data, each data set is stored in one of three CSV files. These files are:

* ImportedAsIsDataChulwalar.csv
* ImportedPlanDataChulwalar.csv
* ImportedIndicatorsChulwalar.csv


###AsIs Chulwalar Data 
``` {r data, child = paste(DataLoad,"/LoadAsIs.rmd",sep = "")}
```

###Plan Chulwalar Data 
``` {r data, child = paste(DataLoad,"/LoadPlan.rmd",sep = "")}
```

###External Indicator Chulwalar Data 
``` {r data, child = paste(DataLoad,"/LoadIndicators.rmd",sep = "")}
```

#Data Cleanup

Data cleanup is imperative to any data analysis. In our precursory view into header/footer records, we can tell there are several items needing to be cleaned across the three datasets. The following sections will walk through cleaning the data to prep for analysis.

###AsIs Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanAsIs.rmd",sep = "")}
```

###Plan Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanPlan.rmd",sep = "")}
```

###External Indicators Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanIndicators.rmd",sep = "")}
```

#Data Analysis

With the data cleaned, we are ready to proceed with our analysis. To recap, while we are interested in forecasting Efak exports for 2014, we are also interested in performing exploratory data analysis to identify potential trends, seasonal fluctuation, and the strength of various correlations.

###Efak Correlation
``` {r data, child = paste(DataAnalysis,"/EfakCorrelation.rmd",sep = "")}
```

###Efak STL
``` {r data, child = paste(DataAnalysis,"/EfakSTL.rmd",sep = "")}
```

###Efak Monthly Seasonal
``` {r data, child = paste(DataAnalysis,"/EfakSeasonal.rmd",sep = "")}
```

###Efak External Indicator Correlation
``` {r data, child = paste(DataAnalysis,"/EfakExtCorrelation.rmd",sep = "")}
```

###Forecasting Efak models with smoothing and related approaches
``` {r data, child = paste(DataAnalysis,"/EfakSmoothing.rmd",sep = "")}
```

#Conclusion

Conclusion Text Goes Here....