---
title: "CaseStudy10_Paper"
author: "Alex Frye, Chris Boomhower"
date: "July 16 2016"
output: md_document
---

```{r DefineDirectory, include=FALSE}
##Change this path per your project root directory on your machine if you wish to regen the CaseStudy10_Paper.md file

###"D:/Documents/School/SMU/2016 Summer/MSDS 6306 - Into to Data Science/Assignments/Week 10/MSDS6306_CaseStudy10_Afrye_CBoomhower"

###"C:\\Users\\Owner\\Documents\\GitHub\\MSDS_6306\\MSDS6306_CaseStudy10_Afrye_CBoomhower"

DefaultDir<-"C:\\Users\\Owner\\Documents\\GitHub\\MSDS_6306\\MSDS6306_CaseStudy10_Afrye_CBoomhower"
DataLoad<-paste(DefaultDir,"/DataLoad",sep = "")
DataCleanup<-paste(DefaultDir,"/DataCleanup",sep = "")
DataAnalysis<-paste(DefaultDir,"/DataAnalysis",sep = "")
RResources<-paste(DefaultDir,"/RResources",sep = "")
###source(paste0(RResources,'/SourceAll.R'))
```


#Introduction

Our client, the Prime Minister of Chulwalar has recruited our small team of SMU data scientists to assist in forecasting Efak (A beautiful flower unique to the region of Chulwalar) exports from his country. He has provided us with historical, as-is flower export data, planned export data, and external key indicators unique to Chulwalar (All historical data provided by month from 2008-2013). It is our duty to best forecast Chulwalar Efak exports in the upcoming year (2014) based on existing export data.

There are several steps needed to accomplish this task. These steps are summarized as follows:

* Load all data sets
* Clean and prepare as-is, planned, and external indicator data for analysis
* Observe correlation between as-is and planned exports
* Plot seasonal and trend decomposition using Loess (STL) for as-is export data
* Plot seasonal trends by month
* Perform exploratory data analysis (EDA) to better understand effects of external indicators
* Utilize smoothing techniques to forecast future exports

###Required Packages

This RMD requires the following R packages to run:

* formattable
* fpp
* ggplot2
* reshape2

```{R Install_Load_Pkgs, message=FALSE, include = FALSE}
#install.packages("formattable")
#install.packages("fpp")
#install.packages("ggplot2")
#install.packages("reshape2")

library(formattable)
library(fpp)
library(ggplot2)
library(reshape2)
```

#Data Load

As this analysis consists of historical export data, plan data, and external indicator data, each data set is stored in one of three CSV files. These files are:

* ImportedAsIsDataChulwalar.csv
* ImportedPlanDataChulwalar.csv
* ImportedIndicatorsChulwalar.csv


###AsIs Chulwalar Data 
``` {r data, child = paste(DataLoad,"/LoadAsIs.rmd",sep = "")}
```

###Plan Chulwalar Data 
``` {r data, child = paste(DataLoad,"/LoadPlan.rmd",sep = "")}
```

###External Indicator Chulwalar Data 
``` {r data, child = paste(DataLoad,"/LoadIndicators.rmd",sep = "")}
```

#Data Cleanup

Data cleanup is imperative to any data analysis. In our precursory view into header/footer records, we can tell there are several items needing to be cleaned across the three data sets. The following sections walk through cleaning the data to prep for analysis.

###AsIs Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanAsIs.rmd",sep = "")}
```

###Plan Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanPlan.rmd",sep = "")}
```

###External Indicators Data Cleanup
``` {r data, child = paste(DataCleanup,"/CleanIndicators.rmd",sep = "")}
```

#Data Analysis

With the data cleaned, we are ready to proceed with our analysis. To recap, while we are interested in forecasting Efak exports for 2014, we are also interested in performing exploratory data analysis to identify potential trends, seasonal fluctuation, and the strength of various correlations.

###Efak Correlation
``` {r data, child = paste(DataAnalysis,"/EfakCorrelation.rmd",sep = "")}
```

###Efak STL
``` {r data, child = paste(DataAnalysis,"/EfakSTL.rmd",sep = "")}
```

###Efak Monthly Seasonal
``` {r data, child = paste(DataAnalysis,"/EfakSeasonal.rmd",sep = "")}
```

###Efak External Indicator Correlation
``` {r data, child = paste(DataAnalysis,"/EfakExtCorrelation.rmd",sep = "")}
```

###Forecasting Efak models with smoothing and related approaches
``` {r data, child = paste(DataAnalysis,"/EfakSmoothing.rmd",sep = "")}
```

#Conclusion

The Prime Minister of Chulwalar requires assistance forecasting Efak exports based on historical as-is data. He has provided not only historical as-is data but also historical export plans and Chulwalar external indicators of interest. Throughout the EDA process in preparation for export forecasting, we've identified additional insightful information beyond a forecast model alone. As-is vs. planned export data has been reviewed as well as seasonal and trend decomposition using Loess for as-is data. Seasonal trend review was extended to a month-by-month comparison across all years (2008-2013), and the effects of external indicators, CEPI and Temperature, were analyzed in particular detail.

EDA produced several insights as mentioned. The first is in regards to correlation between as-is vs. planned Efak exports. The Pearson's r is `0.906`, indicating a strong, positive correlation between as-is and planned exports. This correlation value provides a good baseline for measuring our forecasts at the end of 2014. The second step of analyzing as-is export STL components provides significant insight toward the seasonal behavior surrounding exports. This led to digging deeper into the seasonal trends for as-is exports, resulting in step three. In the third step, month-by-month review confirms consistency in the seasonal trend across the years (primarily a spike early each year followed by a dip during the Summer). Finally, the fourth step provides insight into the association between Efak exports and external indicators. After reviewing all external indicators, the monthly Change in Export Price Index (CEPI) and climate temperatures yield the most interesting results. Like Efak exports, CEPI exhibits a strong positive trend between 2008 and 2014, and it is identified that price index is highest when Efak exports are lowest and vice-versa. Though the Pearson's r (`-0.08`) for the association between Efak exports and temperature is non-indicative of a strong correlation, the seasonal components for exports and temperature confirm our original assumptions that temperature has a negative impact on exports during high temperature months. The reason for a small Pearson's r value is likely caused by a steady mean temperature over the years.

With EDA complete, efforts shift to identify an appropriate forecast model. Various time-series models were analyzed, maximum likelihood estimators, and error measures were compared holistically across all models to assess potential best fit. It is identified that Simple Exponential Smoothing and Holt-Winters' Seasonal Additive models consistently contain lowest values from both MLE and error measures. These indicators led to further analysis of these models. Plotting each model with historical as-is data provides visual insight to not only forecasted values but also model performance as measured against historical exports. Between the Simple Exponential Smoothing and Holt-Winters' Seasonal Additive models, the additive model encompasses the positive correlation and seasonal trends observed in the Chulwalar as-is Efak export data. Due to these factors, the forecast model of choice is the Holt-Winters' Seasonal Additive model. A consultation has been scheduled with the Prime Minister in December of 2014 to assess the accuracy of this forecast and to discuss future forecasting for 2015.